Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-02-18 Paper/Manuscript_Stats&Comp/manuscript_STCO.tex
reduce digits in fig 9

\begin{figure*}
\centering
\begin{tabular}{ c c c c c c c c c c | c c}
\arrayrulecolor{gray}\hline \\[-3mm]
$\ell_{\text{GP}}$ & iter. & $\ell$ & $c$ & $m$ & $\hat{\ell}$ & $\hat{\ell} + 0.01 \geq \ell$ & RMSE & $R^2$ & ELPD & RMSE* & \\ 
%\arrayrulecolor{lightgray}\hline \\[-1mm]
%\multirow{5}{*}{ 0.05} 
% & 1 & 0.50 & 1.60 & 6 & 0.127 & FALSE & 0.800 & 0.264 & -0.980 & 0.748 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 5mm, clip]{fig9_diagnosis_1.png}}\\
% & 2 & 0.127 & 1.20 & 17 & 0.061 & FALSE & 0.427 & 0.779 & -0.396 & 0.330 & \\
% & 3 & 0.061 & 1.20 & 35 & 0.059 & TRUE & 0.264 & 0.908 & 0.008 & 0.063 & \\
% & 4 & 0.053 & 1.20 & 40 & 0.059 & TRUE & 0.254 & 0.915 & 0.088 & 0.029 & \\
% \\[1mm]
\arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{5}{*}{ 0.08} 
 & 1 & 0.50 & 1.60 & 6 & 0.169 & FALSE & 0.447 & 0.610 & -0.396 & 0.360 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 5mm, clip]{fig9_diagnosis_2.png}}\\
 & 2 & 0.169 & 1.20 & 13 & 0.068 & FALSE & 0.357 & 0.738 & -0.176 & 0.242 & \\
 & 3 & 0.068 & 1.20 & 31 & 0.080 & TRUE & 0.242 & 0.871 & 0.204 & 0.013 & \\
 & 4 & 0.058 & 1.20 & 36 & 0.081 & TRUE & 0.241 & 0.871 & 0.207 & 0.009 & \\
 \\[1mm]
 \arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{3}{*}{ 0.13} 
 & 1 & 0.50 & 1.60 & 6 & 0.250 & FALSE & 0.461 & 0.625 & -0.482 & 0.330 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 5mm, clip]{fig9_diagnosis_3.png}}\\
 & 2 & 0.250 & 1.20 & 9 & 0.148 & FALSE & 0.352 & 0.780 & -0.135 & 0.153 & \\
 & 3 & 0.148 & 1.20 & 15 & 0.144 & TRUE & 0.321 & 0.807 & -0.074 & 0.084 & \\
 & 4 & 0.105 & 1.20 & 20 & 0.117 & TRUE & 0.297 & 0.830 & -0.006 & 0.013 & \\
 \\[1mm]
\arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{3}{*}{ 0.25} 
 & 1 & 0.50 & 1.60 & 6 & 0.237 & FALSE & 0.368 & 0.399 & -0.146 & 0.214 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 5mm, clip]{fig9_diagnosis_4.png}}\\
 & 2 & 0.237 & 1.20 & 9 & 0.263 & TRUE & 0.294 & 0.603 & -0.085 & 0.024 & \\
 & 3 & 0.250 & 1.20 & 14 & 0.257 & TRUE & 0.289 & 0.615 & -0.050 & 0.009 & \\
 \\
 \\[1mm]
\arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{3}{*}{ 0.54} 
 & 1 & 0.50 & 1.60 & 6 & 0.376 & FALSE & 0.272 & 0.858 & 0.034 & 0.013 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 3mm, clip]{fig9_diagnosis_5.png}}\\
 & 2 & 0.376 & 1.20 & 6 & 0.469 & TRUE & 0.277 & 0.855 & 0.029 & 0.051 & \\
 & 3 & 0.239 & 1.50 & 11 & 0.525 & TRUE & 0.272 & 0.858 & 0.036 & 0.014 & \\
 \\
 \\[1mm]
\arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{3}{*}{ 0.80} 
 & 1 & 1.00 & 3.20 & 6 & 0.516 & FALSE & 0.286 & 0.923 & 0.133 & 0.025 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 3mm, clip]{fig9_diagnosis_6.png}}\\
 & 2 & 0.516 & 1.65 & 6 & 0.975 & TRUE & 0.286 & 0.923 & 0.107 & 0.030 & \\
 & 3 & 0.496 & 3.12 & 11 & 0.772 & TRUE & 0.283 & 0.924 & 0.109 & 0.005 & \\
 \\
 \\[1mm]
\arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{2}{*}{ 1.40} 
 & 1 & 1.00 & 3.20 & 6 & 1.023 & TRUE & 0.283 & 0.561 & 0.139 & 0.010 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 3mm, clip]{fig9_diagnosis_7.png}}\\
 & 2 & 0.521 & 3.27 & 11 & 1.233 & TRUE & 0.281 & 0.566 & 0.136 & 0.003 & \\
 \\
 \\
 \\[1mm]
 \arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{2}{*}{ 2.94} 
 & 1 & 0.50 & 1.60 & 6 & 1.192 & TRUE & 0.343 & 0.449 & -0.104 & 0.058 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 3mm, clip]{fig9_diagnosis_8.png}}\\
 & 2 & 0.607 & 3.81 & 11 & 2.577 & TRUE & 0.341 & 0.454 & -0.074 & 0.008 & \\
 \\
 \\
 \\[1mm]
\arrayrulecolor{gray}\hline
\end{tabular}
\caption{Diagnosis on various data sets with varying smoothness. RMSE* refers to the root mean squared error computed with the exact GP model as the reference.}
  \label{fig9_diagnosis}
\end{figure*}

>>>>

\begin{figure*}
\centering
\begin{tabular}{ c c c c c c c c c c | c c}
\arrayrulecolor{gray}\hline \\[-3mm]
$\ell_{\text{GP}}$ & iter. & $\ell$ & $c$ & $m$ & $\hat{\ell}$ & $\hat{\ell} + 0.01 \geq \ell$ & RMSE & $R^2$ & ELPD & RMSE* & \\ 
%\arrayrulecolor{lightgray}\hline \\[-1mm]
%\multirow{5}{*}{ 0.05} 
% & 1 & 0.50 & 1.60 & 6 & 0.127 & FALSE & 0.800 & 0.264 & -0.980 & 0.748 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 5mm, clip]{fig9_diagnosis_1.png}}\\
% & 2 & 0.127 & 1.20 & 17 & 0.061 & FALSE & 0.427 & 0.779 & -0.396 & 0.330 & \\
% & 3 & 0.061 & 1.20 & 35 & 0.059 & TRUE & 0.264 & 0.908 & 0.008 & 0.063 & \\
% & 4 & 0.053 & 1.20 & 40 & 0.059 & TRUE & 0.254 & 0.915 & 0.088 & 0.029 & \\
% \\[1mm]
\arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{5}{*}{ 0.08} 
 & 1 & 0.50 & 1.60 & 6 & 0.17 & FALSE & 0.45 & 0.61 & -0.40 & 0.36 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 5mm, clip]{fig9_diagnosis_2.png}}\\
 & 2 & 0.17 & 1.20 & 13 & 0.07 & FALSE & 0.36 & 0.74 & -0.18 & 0.24 & \\
 & 3 & 0.07 & 1.20 & 31 & 0.08 & TRUE & 0.24 & 0.87 & 0.20 & 0.01 & \\
 & 4 & 0.06 & 1.20 & 36 & 0.08 & TRUE & 0.24 & 0.87 & 0.21 & 0.01 & \\
 \\[1mm]
 \arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{3}{*}{ 0.13} 
 & 1 & 0.50 & 1.60 & 6 & 0.25 & FALSE & 0.46 & 0.63 & -0.49 & 0.33 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 5mm, clip]{fig9_diagnosis_3.png}}\\
 & 2 & 0.25 & 1.20 & 9 & 0.15 & FALSE & 0.35 & 0.78 & -0.14 & 0.15 & \\
 & 3 & 0.15 & 1.20 & 15 & 0.15 & TRUE & 0.32 & 0.81 & -0.07 & 0.08 & \\
 & 4 & 0.11 & 1.20 & 20 & 0.12 & TRUE & 0.30 & 0.83 & -0.01 & 0.01 & \\
 \\[1mm]
\arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{3}{*}{ 0.25} 
 & 1 & 0.50 & 1.60 & 6 & 0.24 & FALSE & 0.37 & 0.40 & -0.15 & 0.21 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 5mm, clip]{fig9_diagnosis_4.png}}\\
 & 2 & 0.24 & 1.20 & 9 & 0.26 & TRUE & 0.30 & 0.60 & -0.09 & 0.02 & \\
 & 3 & 0.25 & 1.20 & 14 & 0.26 & TRUE & 0.29 & 0.62 & -0.05 & 0.01 & \\
 \\
 \\[1mm]
\arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{3}{*}{ 0.54} 
 & 1 & 0.50 & 1.60 & 6 & 0.38 & FALSE & 0.27 & 0.86 & 0.03 & 0.01 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 3mm, clip]{fig9_diagnosis_5.png}}\\
 & 2 & 0.38 & 1.20 & 6 & 0.47 & TRUE & 0.28 & 0.86 & 0.03 & 0.05 & \\
 & 3 & 0.24 & 1.50 & 11 & 0.53 & TRUE & 0.27 & 0.86 & 0.04 & 0.01 & \\
 \\
 \\[1mm]
\arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{3}{*}{ 0.80} 
 & 1 & 1.00 & 3.20 & 6 & 0.52 & FALSE & 0.29 & 0.92 & 0.13 & 0.03 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 3mm, clip]{fig9_diagnosis_6.png}}\\
 & 2 & 0.52 & 1.65 & 6 & 0.98 & TRUE & 0.29 & 0.92 & 0.11 & 0.03 & \\
 & 3 & 0.50 & 3.12 & 11 & 0.77 & TRUE & 0.28 & 0.92 & 0.11 & 0.01 & \\
 \\
 \\[1mm]
\arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{2}{*}{ 1.40} 
 & 1 & 1.00 & 3.20 & 6 & 1.02 & TRUE & 0.28 & 0.56 & 0.14 & 0.010 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 3mm, clip]{fig9_diagnosis_7.png}}\\
 & 2 & 0.52 & 3.27 & 11 & 1.23 & TRUE & 0.28 & 0.57 & 0.14 & 0.00 & \\
 \\
 \\
 \\[1mm]
 \arrayrulecolor{lightgray}\hline \\[-1mm]
\multirow{2}{*}{ 2.94} 
 & 1 & 0.50 & 1.60 & 6 & 1.19 & TRUE & 0.34 & 0.45 & -0.10 & 0.06 & \multirow{5}{*}{ \includegraphics[scale=0.20, trim = 0mm 10mm 0mm 3mm, clip]{fig9_diagnosis_8.png}}\\
 & 2 & 0.61 & 3.81 & 11 & 2.58 & TRUE & 0.34 & 0.45 & -0.07 & 0.01 & \\
 \\
 \\
 \\[1mm]
\arrayrulecolor{gray}\hline
\end{tabular}
\caption{Diagnosis on various data sets with varying smoothness. RMSE* refers to the root mean squared error computed with the exact GP model as the reference.}
  \label{fig9_diagnosis}
\end{figure*}
